---
title: "02 Descriptive Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Packages
```{r}
library(readr)
library(dplyr)
library(stringr)
library(tidyr)
library(tidyverse)
#scaling the exase
library("scales")
```

# Read Data
```{r}
# Read data
vehicles <- read_csv("data/cars_processed.csv")

# Convert chr columns to factors 
factor_column_names <- colnames(vehicles %>% select(where(is.character)))
vehicles[, factor_column_names] <- lapply(vehicles[,factor_column_names], factor)

# Features for EDA
vehicles_lr <- vehicles %>% select(-c(year, selling_price, selling_price_binary))

#Change the order of columns
vehicles_lr <- vehicles_lr[, c(1,2,3,4,5,6,7,8,9,10,12,11)]

head(vehicles)
```




**Distribution of Selling Price in Dollars**

```{r}
hist <- ggplot(data = vehicles, aes(x=selling_price_dollars)) +
geom_histogram(color="black", fill="lightblue", boundary=0, binwidth = 5000, closed="left") +
#scale_y_continuous(limits=c(0,500), expand=c(0,0)) +
  scale_x_continuous(labels = comma)
labs(title="Distribution of Selling Price in Dollars",x="Selling price in dollars", y="Frequency") +
theme_classic() 

mytheme <- theme(
axis.line.y=element_blank(),
axis.text.y=element_blank(),
axis.ticks.y=element_blank(),
axis.title.y=element_blank()
)

box <- ggplot(data = vehicles, aes(y=selling_price_dollars)) +
geom_boxplot(color="black",fill="lightblue", outlier.shape=21, outlier.fill="lightblue", outlier.alpha=0.3) +
  scale_x_continuous(labels = comma) +
coord_flip() + theme_classic() + mytheme +
theme(
axis.line.x=element_blank(),
axis.text.x=element_blank(),
axis.ticks.x=element_blank(),
axis.title.x=element_blank()
)

library(cowplot)
plot_grid(hist, box, ncol = 1, rel_heights = c(0.85, 0.15), align = 'v', axis = 'lr')

```

**The Distribution of Binary Selling Price**

```{r}
vehicles$selling_price_binary <- factor(vehicles$selling_price_binary, c("Yes", "No"))

library(RColorBrewer)
mycols <- brewer.pal(8, "Accent")[2:3]


ggplot(data=vehicles, aes(x=selling_price_binary)) +
labs(title="Distribution of Binary Selling Price",x="Binary selling price", y="Frequency") +
scale_y_continuous(expand=c(0,0)) +
coord_cartesian(ylim=c(0,7000)) +
geom_bar(aes(fill=selling_price_binary)) +
  scale_fill_manual(values=mycols)



```


**Distribution of Selling Price in Dollars by km driven**

```{r fig.width=5}
scat <- ggplot(vehicles, aes(x=km_driven, y=selling_price_dollars, color=selling_price_binary)) + 
  geom_point(size=2) + 
  labs(title="Distribution of Selling Price in Dollars by km driven",x="KM Driven", y=" Selling Price in Dollars")+ 
  scale_y_continuous(labels = comma)

mytheme <- theme(
axis.line.y=element_blank(),
axis.text.y=element_blank(),
axis.ticks.y=element_blank(),
axis.title.y=element_blank()
)

box <- ggplot(data = vehicles, aes(y=km_driven)) +
geom_boxplot(color="black",fill="lightblue", outlier.shape=21, outlier.fill="lightblue", outlier.alpha=0.3) +
  scale_x_continuous(labels = comma) +
coord_flip() + theme_classic() + mytheme +
theme(
axis.line.x=element_blank(),
axis.text.x=element_blank(),
axis.ticks.x=element_blank(),
axis.title.x=element_blank()
)

library(cowplot)
plot_grid(scat, box, ncol = 1, rel_heights = c(0.85, 0.15), align = 'v', axis = 'lr')
```


__Second Plot__

```{r}
library(ggpubr)
ggscatterhist(
  vehicles, x = "km_driven", y = "selling_price_dollars", color= "selling_price_binary",
  margin.plot = "boxplot",
  title = "Distribution of Selling Price in Dollars by km driven",
  xlab = "KM Driven",
  ylab = "Selling Price in Dollars",
  bins=15,
  margin.params = list(fill = "lightblue", outlier.shape=1)
)
```


**Distribution of Selling Price in Dollars by Year**

```{r fig.width=5}
library("scales")

ggplot(vehicles, aes(x=year, y=selling_price_dollars, color=selling_price_binary)) + 
  geom_point(size=2) + 
  labs(title="Distribution of Selling Price in Dollars by Year",x="Year", y=" Selling Price in Dollars") +
  scale_y_continuous(labels = comma)
#+
 # coord_cartesian(ylim = c(0, 20000))
```





# Correlation Matrix 

```{r}
vehicles_cor <- vehicles_lr %>% select(-c(Make, fuel, seller_type, transmission, owner))

# Correlation matrix
cor_mat <- round(cor(vehicles_cor),2)

#Get upper triangle
get_upper_tri <- function(cormat){
    cormat[lower.tri(cormat)]<- NA
    return(cormat)
}

upper_tri <- get_upper_tri(cor_mat)

# Melt the correlation matrix
library(reshape2)
melted_cormat <- melt(upper_tri, na.rm = TRUE)

# Heatmap
library(ggplot2)
ggheatmap <- ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, vjust = 1,
                                   size = 12, hjust = 1))+
  coord_fixed()


#Heatmap with values
ggheatmap + 
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 4) +
theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.grid.major = element_blank(),
  panel.border = element_blank(),
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  legend.justification = c(1, 0),
  legend.position = c(0.6, 0.7),
  legend.direction = "horizontal")+
  guides(fill = guide_colorbar(barwidth = 7, barheight = 1,
                title.position = "top", title.hjust = 0.5))
```


# Distribution of Categorical Variables


**selling price in dollars ~ fuel**



```{r}
vehicles_lr$fuel <- factor(vehicles_lr$fuel, c("Diesel", "Petrol", "CNG", "LPG"))

ggplot(data=vehicles_lr, aes(x=fuel, y=selling_price_dollars, fill=fuel)) +
geom_boxplot() +
guides(fill="none")+
  scale_y_continuous(labels = comma)+
    labs(title="Distribution of Selling Price in Dollars by Fuel",x="Fuel", y=" Selling Price in Dollars") 
```

**selling price in dollars ~ fuel : zoomed in**

```{r}
ggplot(data=vehicles_lr, aes(x=fuel, y=selling_price_dollars, fill=fuel)) +
geom_boxplot() +
coord_cartesian(ylim = c(0, 20000)) +
guides(fill="none") +
    scale_y_continuous(labels = comma)+
    labs(title="Distribution of Selling Price in Dollars by Fuel",x="Fuel", y=" Selling Price in Dollars") 
```

**selling price in dollars ~ transmission**

```{r}
ggplot(data=vehicles_lr, aes(x=transmission, y=selling_price_dollars, fill=transmission)) +
geom_boxplot() +
#coord_cartesian(ylim = c(0, 50000)) +
guides(fill="none") +
    scale_y_continuous(labels = comma)+
    labs(title="Distribution of Selling Price in Dollars by Transmission",x="Transmission", y=" Selling Price in Dollars") 
```

**selling price in dollars ~ seller type : zoomed in**
```{r}
ggplot(data=vehicles_lr, aes(x=seller_type, y=selling_price_dollars, fill=seller_type)) +
geom_boxplot() +
coord_cartesian(ylim = c(0, 50000)) +
guides(fill="none") +
  scale_y_continuous(labels = comma)+
  labs(title="Distribution of Selling Price in Dollars by Seller Type",x="Seller Type", y=" Selling Price in Dollars") 

```



**selling price in dollars ~ owner : zoomed in**

```{r}
vehicles_lr$owner <- factor(vehicles_lr$owner,     # Reorder factor levels
                         c("First Owner", "Second Owner", "Third Owner", "Fourth & Above Owner", "Test Drive Car"))
ggplot(data=vehicles_lr %>% filter(owner %in% c("First Owner", "Second Owner", "Third Owner", "Fourth & Above Owner")), aes(x=owner, y=selling_price_dollars, fill=owner)) +
geom_boxplot() +
coord_cartesian(ylim = c(0, 20000)) +
guides(fill="none") +
   scale_y_continuous(labels = comma)+
  labs(title="Distribution of Selling Price in Dollars by Owner",x="Owner", y=" Selling Price in Dollars") 

```

